SU($n$) ferromagnets near the Heisenberg point

### 2021-04-01 collective_sun/sun_perturbation.tex
fix minor error in SU(n) perturbation theory notes

The process of constructing and simplifying diagrams to compute scalar
coefficients of the expansions in \eqref{eq:sym_prod_diagrams} and
\eqref{eq:sum_diagrams_alt} is systematic enough to perform
algorithmically.  The last step necessary to automate the evaluation
of these expansions is the projection of multi-spin operators
$\ot{\m X}\p{\ell}$ onto the PS manifold $\M_0$.  Without loss of
generality, we consider a single $M$-spin operator $X$.  Our task is
essentially to find coefficients of the expansion
\begin{align}
  \P_0 X \P_0
  = \sum_{a,b\in\A_n\p{N}} \bk{a|X|b} \op{a}{b},
\end{align}
where $\A_n\p{N}$ is the set of all ways to assign $N$ (identical)
spins to $n$ (distinct) states, such that for any $a\in\A_n\p{N}$, the
state $\ket{a}=\ket{a_1,a_2,\cdots,a_n}$ is labeled by the occupation
number $a_\mu$ of state $\mu$, with $\sum_\mu a_\mu = N$.  Written out
explicitly,
\begin{align}
  \ket{a} = \f1{\sqrt{\C\p{a}}}
  \sum_{\substack{\t{distinct}\\\t{permutations}\\\Pi~\t{of}~\tilde a}}
  \Pi \ket{\tilde a},
  &&
  \ket{\tilde a} \equiv \bigotimes_\mu \ket{\mu}^{\otimes a_\mu},
  &&
  \C\p{a} \equiv \f{\p{\sum_\mu a_\mu}!}{\prod_\nu a_\nu!},
\end{align}
where the multinomial coefficient $\C\p{a}$ counts the number of
distinct ways to permute the tensor factors of $\ket{\tilde a}$, and
enforces $\bk{a|a}=1$.  Using these states, we can expand
\begin{align}
  \bk{a|X|b}
  = \sum_{\substack{\alpha,\beta\in\A_n\p{M}\\\alpha\le a,\,\beta\le b}}
  \delta_{a-\alpha,b-\beta}
  \sqrt{\f{\C\p{\alpha}\C\p{a-\alpha}\C\p{\beta}\C\p{b-\beta}}
    {\C\p{a}\C\p{b}}}
  \bk{\alpha|X|\beta},
  \label{eq:multi_body_eval}
\end{align}
where the restriction $\alpha\le a$ and difference $a-\alpha$ are
evaluated element-wise, i.e.~$\alpha<a\implies \alpha_\mu\le a_\mu$
and $\p{a-\alpha}_\mu=a_\mu-\alpha_\mu$ for all $\mu$; and
$\delta_{cd}=1$ if $c=d$ and zero otherwise.  We sum over both
$\alpha$ and $\beta$ above merely to keep the expression symmetric
with respect to transposition; in practice, one can simply sum over
$\alpha\in\A_n\p{M}$ and set $\beta=b-a+\alpha$ (throwing out terms
with any $\beta_\mu<0$).  Note that, by slight abuse of notation, the
operator $X$ on the left of \eqref{eq:multi_body_eval} acts on an
arbitrary choice of $M$ spins (out of $N$), whereas the operator $X$
on the right of \eqref{eq:multi_body_eval} is simply an $M$-spin
operator, with matrix elements $\bk{\alpha|X|\beta}$ evaluated with
respect to the $M$-spin states $\ket\alpha,\ket\beta$.

>>>>

The process of constructing and simplifying diagrams to compute scalar
coefficients of the expansions in \eqref{eq:sym_prod_diagrams} and
\eqref{eq:sum_diagrams_alt} is systematic enough to perform
algorithmically.  The last step necessary to automate the evaluation
of these expansions is the projection of multi-spin operators
$\ot{\m X}\p{\ell}$ onto the PS manifold $\M_0$.  Without loss of
generality, we consider a single $M$-spin operator $X$.  Our task is
essentially to find coefficients of the expansion
\begin{align}
  \P_0 X \P_0
  = \sum_{a,b\in\A_n\p{N}} \bk{a|X|b} \op{a}{b},
\end{align}
where $\A_n\p{N}$ is the set of all ways to assign $N$ (identical)
spins to $n$ (distinct) states, such that for any $a\in\A_n\p{N}$, the
state $\ket{a}=\ket{a_1,a_2,\cdots,a_n}$ is labeled by the occupation
number $a_\mu$ of state $\mu$, with $\sum_\mu a_\mu = N$.  Written out
explicitly,
\begin{align}
  \ket{a} = \f1{\sqrt{\C\p{a}}}
  \sum_{\substack{\t{distinct}\\\t{permutations}\\\Pi~\t{of}~\tilde a}}
  \Pi \ket{\tilde a},
  &&
  \ket{\tilde a} \equiv \bigotimes_\mu \ket{\mu}^{\otimes a_\mu},
  &&
  \C\p{a} \equiv \f{\p{\sum_\mu a_\mu}!}{\prod_\nu a_\nu!},
\end{align}
where the multinomial coefficient $\C\p{a}$ counts the number of
distinct ways to permute the tensor factors of $\ket{\tilde a}$, and
enforces $\bk{a|a}=1$.  Using these states, we can expand
\begin{align}
  \bk{a|X|b}
  = \sum_{\substack{\alpha,\beta\in\A_n\p{M}\\\alpha\le a,\,\beta\le b}}
  \delta_{a-\alpha,b-\beta}
  \sqrt{\f{\C\p{\alpha}\C\p{a-\alpha}\C\p{\beta}\C\p{b-\beta}}
    {\C\p{a}\C\p{b}}}
  \bk{\alpha|X|\beta},
  \label{eq:multi_body_eval}
\end{align}
where the restriction $\alpha\le a$ and difference $a-\alpha$ are
evaluated element-wise, i.e.~$\alpha\le a\implies \alpha_\mu\le a_\mu$
and $\p{a-\alpha}_\mu=a_\mu-\alpha_\mu$ for all $\mu$; and
$\delta_{cd}=1$ if $c=d$ and zero otherwise.  We sum over both
$\alpha$ and $\beta$ above merely to keep the expression symmetric
with respect to transposition; in practice, one can simply sum over
$\alpha\in\A_n\p{M}$ and set $\beta=b-a+\alpha$ (throwing out terms
with any $\beta_\mu<0$).  Note that, by slight abuse of notation, the
operator $X$ on the left of \eqref{eq:multi_body_eval} acts on an
arbitrary choice of $M$ spins (out of $N$), whereas the operator $X$
on the right of \eqref{eq:multi_body_eval} is simply an $M$-spin
operator, with matrix elements $\bk{\alpha|X|\beta}$ evaluated with
respect to the $M$-spin states $\ket\alpha,\ket\beta$.
